Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-06 paper.tex
articles, capitalization

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                    Challenges in Co-verification 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The verification of FW given in C/C++ together with the RTL given in a hardware
description language (HDL) such as Verilog/VHDL is a challenging task due to 
few reasons -- 1) the timing and semantic mismatch between the synchronous
clock-driven HW model and asynchronous event-driven SW model -- for example,
FW running on a processor could be much faster than the HW
model it interacts with, 2) lack of support for property specification in 
HW/FW co-designs that can precisely capture the design intent of the 
communication between HW and FW, 3) Large
number of interleavings between HW and FW threads, and 4) lack 
of automated formal tools that support co-designs implemented in C/C++ and 
Verilog/VHDL.   In this paper, we address some of these challenges to enable
seamless adoption of formal techniques in hardware/software co-verification.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                    Challenges in Co-verification 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The verification of a FW given in C/C++ together with an RTL given in a hardware
description language (HDL) such as Verilog/VHDL is a challenging task due to a
few reasons -- 1) the timing and semantic mismatch between the synchronous
clock-driven HW model and asynchronous event-driven SW model. For example, the
FW running on a processor could be much faster than the HW
model it interacts with, 2) lack of support for property specification in 
HW/FW co-designs that can precisely capture the design intent of the 
communication between HW and FW, 3) large
number of interleavings between HW and FW threads, and 4) lack 
of automated formal tools that support co-designs implemented in C/C++ and 
Verilog/VHDL.   In this paper, we address some of these challenges to enable
seamless adoption of formal techniques in hardware/software co-verification.
